\normalfont \normalsize \textsc{university, school or department name} \\ [25pt] \horrule{0.5pt} \\[0.4cm] \huge Assignment Title \\ \horrule{2pt} \\[0.5cm]

### 2013-01-27 exercise3/Paper/paper.tex
minor changes

\title{	
\normalfont \normalsize 
\textsc{university, school or department name} \\ [25pt] % Your university, school and/or department name(s)
\horrule{0.5pt} \\[0.4cm] % Thin top horizontal rule
\huge Assignment Title \\ % The assignment title
\horrule{2pt} \\[0.5cm] % Thick bottom horizontal rule
}

\author{John Smith} % Your name

@@

If we raise the K-paramter up to 100, we get worse results. As seen in figure \ref{fig:skin:predicted:k100} the K-NN algorithm misclassfies more instances that are located in one corner of the RGB space. Hence, we can see more white marks in figure \ref{fig:skin:correct:k100}.

@@

\subsection{Data Sets}
\todo[inline]{Wich data sets did we used?}
\end{document}

>>>>

\title{	
\normalfont \normalsize 
\textsc{Vienna University of Technology} \\ [25pt] % Your university, school and/or department name(s)
\horrule{0.5pt} \\[0.4cm] % Thin top horizontal rule
\huge Demonstration of K-Nearest-Neighbor \\ % The assignment title
\horrule{2pt} \\[0.5cm] % Thick bottom horizontal rule
}

\author{Benjamin Kiesl \and Philipp Steinwender \and Robert Schäfer} % Your name

@@

If we raise the K-parameter up to 100, we get worse results. As seen in figure \ref{fig:skin:predicted:k100} the K-NN algorithm misclassfies more instances that are located in one corner of the RGB space. Hence, we can see more white marks in figure \ref{fig:skin:correct:k100}.

@@

\end{document}
